### 2016-02-15 README.Rmd
added `sort_type`
`sort_type` is a default which sorts the columns by type. This makes it
easier to see the groups of data.

Examples were added to README
changed sort_cols to sort_miss

The classes are represented on the legend, and missing data represented by grey. This tells us that R reads this dataset as having numeric and integer values, along with some missing data in `Ozone` and `Solar.R`.

@@

You can further cluster the missingness and arrange the columns by missingness by setting `cluster = TRUE` and `sort_cols = TRUE`.

@@

vis_miss(airquality, 
         cluster = TRUE,
         sort_cols = TRUE)

>>>>

The classes are represented on the legend, and missing data represented by grey.

by default, `vis_dat` sorts the columns according to the type of the data in the vectors. You can turn this off by setting `sort_type == FALSE`. Perhaps this feature is better illustrated using the `example2` dataset, borrowed from csv-fingerprint

```{r}

vis_dat(example2)

vis_dat(example2, 
        sort_type = FALSE)

This tells us that R reads this dataset as having numeric and integer values, along with some missing data in `Ozone` and `Solar.R`.

@@

You can further cluster the missingness and arrange the columns by missingness by setting `cluster = TRUE` and `sort_miss = TRUE`.

@@

vis_miss(airquality, 
         cluster = TRUE,
         sort_miss = TRUE)
